---
title: "Set up VR Analysis"
author: "Laurent Smeets"
date: "13 december 2018"
output: html_document
---
This document explains the set up of the R code that is used to distill features from the VR files.


## Set up Parameters

As a first step it is important to define certain parameters in the **config.R** file. In this short file different parameters are controlled.

### 1) Image

Use this line to name the image which will form the background of the plots. This image has to be in the folder named *input*.

```{r, eval=F, echo=T}
img.name = 'Supermarkt2.png',
```

### 2) Input/output folders

Use these 3 lines to set the name of folder with the input files, and the name of the folder where the output will go. This folders has to be within the folder named *input*.

```{r, eval=F, echo=T}
  # directory with input files
  input.dir = "test",
  # directory with output files
  output.dir = "test2",
```

### 3) Saving options

Here you can control what time of files you would like to save as output.

```{r, eval=F, echo=T}
  raw.images    = TRUE,     # Images with just the path
  full.images   = TRUE,     # Images with path + aisles, stops, crosses, etc.
  save.data     = TRUE,     # should stops, slows etc. be saved.
  save.to.excel = FALSE,    # should stops, slows etc. be saved.to an excel file
  make.gif      = FALSE,    # Gif of a path (DOES NOT WORK RIGHT NOW)
```

### 4) Ecel sheet parameters

These 4 lines of code are used to make sure R reads the excel file with data on the respondents correctly. You set on which sheet are the data points related to analysis (hits, time, avatar, etc.), on which sheets are the personal data, on which sheet is the NPO data, and how many rows of data points there are (number of respondents). We also define in which range of the excel sheet is relevant data and which range there is information R does not ned to load.

```{r, eval=F, echo=T}
  sheet.excel  = 2,        # On which sheet are the data point
  sheet.excel2 = 1,        # On which sheet are the personal data
  sheet.excel3 = 3,        # On which sheet are the NPO data
  n.row.excel  = 74,       # How many rows of data points are there
  
  range.personal = "A1:H",
  range.NPO      = "A1:V",
```

### 5) Stop, slow, and crossing parameters

Here you set the parameters that define a stop, slow, and crossing.

```{r, eval=F, echo=T}
    # Stops measures the amount of stops. A stop is defined as less than 
    # stop.radius movement in at least stop.time from a point
    stops = list(
      stop.time = 2,      # seconds of stopping
      stop.radius = 0.25  # meters of walking
    ),
    
    # Slows measures the times someone has slowed. Is defined the same as a
    # stop, but with different numbers
    slows = list(
      slow.time = 4,   # seconds of stopping
      slow.radius = 1    # meters of walking
    ),
    
    # Crossings
    cross = list(
      cross.lag1 = 3, #Time required for a path to cross itself before it counts as a crossing
      cross.lag2 = 3  #Minimum time required between two crossings
    ),
```

### 6) Products and aisles

Here you can set up where in the VR supermarket different products can be found and how the supermarket looks like.
First set the max number of products in the supermarket, then we list where the different aisles are, based on the design of the supermarket, and then we assign the the location of the products.

```{r, eval=F, echo=T}
number.of.items = 8,  # total number of items in supermarket people can pick up.
    
    # Aisles, both names and coordinates are defined here
    aisles = data.frame(xmin = c(rep(c(5, 9.2, 13, 17, 21), 2), 25.2, rep(5,3)),
                        xmax = c(rep(c(8.5, 12.3, 16.3, 20.3, 24.5), 2), 29.3, c(24.5 , 29.3, 29.3)),
                        zmin = c(rep(-37.5, 5), rep(-24.9, 6), c(-42, -30.2, -13.8)),
                        zmax = c(rep(-30.3, 5), rep(-13.9, 6),  c(-37.6, -25, -10)), 
                        aisle.names = c(paste0(rep(1:5, 2), rep(LETTERS[1:2], each = 5)), "6B", "M1", "M2", "M3"), # Names of aisles
                        x = 1, y = 1, colour = 1, # Required for gg plot to work (don't ask why)
                        type= c(rep("shopping", 11), rep("main", 3))),
    
    
    #These are the exact locations of the product
    products = data.frame(x =             c( 16.3,  17.2,   13.1,   24.3,   12.3,  24.3,   8.3,   12.9     ),  
                          z =             c(-18.3, -34.4,  -32.9,  -17.2,  -37.2, -15.6,  -21.9, -37.9     ),
                          height =        c(3.3,    3.3,    3.3,    3.3,    3.3,   3.3,    3.3,  .3        ),
                          width =         c(1.5,   1.5,    1.5,    1.5,    1.5,    1.5,   1.5,    3.3        ),
                          up.down.side =  c("up", "down", "down" , "up",   "up",   "up",   "up", "sideleft"),
                          announced =     c(FALSE, FALSE,  FALSE,  FALSE,  FALSE,  FALSE,  FALSE, TRUE     ),
                          productnumber = c("P1",   "P2",  "P3",    "P4",   "P5",  "P6",  "P7",   "P8"     ),
                          x = 1, y = 1, colour = 1)
    # possible value for up.down.side: "up", "down", "sideleft", "sideright"
```


## Run analysis

To run the analysis open the **Run.R** file in the *code* folder. 


### 1) Set working directory 

If you copied the code from Github and did not fork the project.R file you have to set a working directory:

```{r, eval=F, echo=T}
setwd("C:/Users/etc/etc/etc)
```

### 2) Install and load packages
 

Now we can load the packages we need for the code 

```{r, eval=F, echo=T}
packages <- c("jsonlite", "tidyverse", "png", "ggforce",
              "ggalt", "Rcpp", "grid", "gganimate")
lapply(packages, require, character.only = TRUE)

```


### 3) Load features

With this code we load all the R code and functions that are used to create features, the code for these functions is stored in the folder *features* (inside the folder *code*). We also load the configuration file, we defined above

```{r, eval=F, echo=T}
source("code/config.R") # load the configuration file
sapply(list.files("code/features", full.names = TRUE, '.R'), source) # load FE funcs
sourceCpp('code/features/cppDoLinesIntersect.cpp') # load the C function that calculates crossings
```

### 4) load the data

With this code we first load the image we use as background for the plots. Secondly we create a list with the names of all the JSON data files with the raw location data from the VR study. Thirdly we load the Excel sheet of the Excel document with the hits of the respondents. 

```{r, eval=F, echo=T}
# Load image
image <- readPNG(paste0('input/', params$img.name))

# get data files
data.files <- list.files(
  path = file.path("input", params$input.dir),
  pattern = 'json',
  full.names = FALSE
)

# get the excel sheet
data.files2 <- list.files(
  path = file.path("input", params$input.dir),
  pattern = 'xlsx',
  full.names = FALSE
)

# load the excelsheet with the hits of the respondents
Excel<-readxl::read_excel(path= file.path("input", params$input.dir, data.files2), 
                                          sheet=params$sheet.excel,
                                          n_max=params$n.row.excel)


```



### 5) Create an empty data set.

Now we create an empty data table with on the rows all the respondents and in the collumns the different features we distinguish.

```{r, eval=F, echo=T}
# Create data frame to save results
data <- createDataFrame(data.files)
```


### 6) Run the code of the features 

By using a `for loop` over the different respondents we run the different function that are used to create features over the respondents one by one

```{r, eval=F, echo=T}

# loop over all the participants 
for(i in 1 : length(data.files)){
  JSONfile <- data.files[i]
  
  res <- runFirstAnalyses(JSONfile = JSONfile, image = image, 
                          raw.images = params$raw.images, 
                          save.data = params$save.data, 
                          data = data,
                          input.dir = params$input.dir, 
                          output.dir = params$output.dir,
                          products = params$features$products,
                          i = i)
  
  if(params$save.data | params$full.images){
    res.aisles <- getAisleTimes(data = res$data,
                                FootPosition = res$FootPosition,
                                time = res$time,
                                gg = res$gg,
                                aisles = params$features$aisles,
                                full.images = params$full.images,
                                save.data = params$save.data,
                                i = i)
    
    res.cross <- getCrossings(data = res.aisles$data,
                              FootPosition = res$FootPosition,
                              time = res$time,
                              gg = res.aisles$gg.aisles,
                              shopping.aisle.time.points = res.aisles$shopping.aisle.time.points,
                              aisles = params$features$aisles,
                              cross.lag1 = params$features$cross$cross.lag1,
                              cross.lag2 = params$features$cross$cross.lag2,
                              full.images = params$full.images,
                              i = i)
    
    res.stops <- getStops(data = res.cross$data,
                          FootPosition = res$FootPosition,
                          time = res$time,
                          gg = res.cross$gg.cross,
                          stop.time = params$features$stops$stop.time,
                          stop.radius = params$features$stops$stop.radius,
                          full.images = params$full.images,
                          productsbox = res$productbox,
                          save.data = params$save.data,
                          i = i)
    
    res.products <- WalkpastProduct(data = res.stops$data,
                                   FootPosition = res$FootPosition,
                                   time = res$time,
                                   gg = res.stops$gg,
                                   products =  res$productbox,
                                   products2 = params$features$products, 
                                   full.images = params$full.images,
                                   save.data = params$save.data,
                                   i = i)
    
    res.slows <- getSlows(data = res.products$data, 
                          FootPosition = res$FootPosition, 
                          time = res$time, 
                          gg = res.products$gg.products,
                          stop.points = res.stops$stop.points, 
                          slow.time = params$features$slows$slow.time, 
                          slow.radius = params$features$slows$slow.radius,
                          producttimepoint.time.points = res.products$producttimepoint.time.points,
                          full.images = params$full.images,
                          save.data = params$save.data, 
                          i = i)
    data <- res.slows$data  
```

### 7) Create the plots

This part of the code is used to create the plots, if we defined in the *config.R* file that we want to save the plots.

```{r, eval=F, echo=T}

if(params$full.images){
      if( ! file.exists(paste0('output/png/', params$output.dir))){
        dir.create(paste0('output/png/', params$output.dir))
      }
      # Save variables required for ggplot in global environment 
      # (ggplot cannot handle variables created in functions)
      aisles <- params$features$aisles
      aisles2 <- params$features$aisles2
      n.crossings <- res.cross$n.crossings
      stop.radius <- params$features$stops$stop.radius
      n.stops <- res.stops$n.stops
      n.stops.before.item<-res.stops$n.stops.before.item
      n.slows <- res.slows$n.slows
      n.slows.before.item<-res.slows$n.slows.before.item
      productsbox <- params$features$products1
      productslocation <- params$features$products2
      
      #JSONfile <- substr(JSONfile, 1, 21)
      ggsave(paste0('output/png/', params$output.dir, '/', JSONfile, '.png'), 
      res.slows$gg.slows, width = 37.5, height = 21, units = 'cm')
    }
  }
}

```



### 8) Enrich data 

This code makes sure that the personal and NPO data is correctly loaded and attached to the data table with all the features of the respondents.

```{r, eval=F, echo=T}
# merge data from other excel sheets with other test results
Excel.personal <- readxl::read_excel(path = file.path("input", params$input.dir, data.files2), 
                                     sheet = params$sheet.excel2,
                                     range = paste0(params$range.personal, params$n.row.excel))

Excel.NPO<-readxl::read_excel(path  = file.path("input", params$input.dir, data.files2), 
                              sheet = params$sheet.excel3,
                              range = paste0(params$range.NPO, params$n.row.excel))


# for some reason distance doesnt really work yet so it is calculated here
datamerged <- 
  left_join(data, select(Excel.personal, -VR_aborted, -Avatars), by = "ID" ) %>%
  left_join(select(Excel.NPO, -education, -age), by = "ID" ) %>% 
  mutate(distance = total.time*average.speed)

```


### 9) Save data set

This coad can be used to save final data table as a csv

```{r, eval=F, echo=T}
# save the data to an excel sheet
if(params$save.to.excel){
  write.csv2(datamerged, file = "output/csv/data6.csv", row.names = FALSE)
}
```

